Loop-Aware Optimizations in PyPy's Tracing JIT

### 2011-06-21 talk/iwtc11/paper.tex
let the image class choose interpolation method, making multiple magnify() implemenattions unnecessery

The current approach still has some limitations which we plan to address in the
future. In particular loop peeling works poorly in combination with trace
trees or trace stitching. The side exits attached guards that fail often
currently have to jump to the preamble which makes loops with several equally
common paths less efficient than they could be.

>>>>

The current approach still has some limitations which we plan to lift in the
future. In particular loop peeling is working less well in combination with
trace trees or trace stitching. The side exits attached guards that fail often
currently have to jump to the preamble which makes loops with several equally
common paths less efficient than they could be.
